\chapter{Introduction}

\textbf{Davinci} is a scientific software for the visualization and processing of single-crystal diffraction data measured with a point detector.

%===========================================================
\section{What is Davinci for?}
%===========================================================

\textbf{Davinci} allows to obtain the squares of the structure factors  ($F^2_\text{obs}$) based on the calculation of integrated intensities of the measured Bragg peaks. In the case of polarised neutron diffraction measurements, \textbf{Davinci} calculates the flipping ratios (FR). These data are necessary for crystal and magnetic structure determination with the crystallographic software, such as \textbf{FullProf}, \textbf{Jana2006}, \textbf{ShelX}, etc.

%===========================================================
\section{Davinci features}
%===========================================================
\begin{itemize}
	\item \itemtitle{Cross-platform}
		\textbf{Davinci} works across operating systems. You can download precompiled binaries of \textbf{Davinci Installer} for \textbf{macOS}, \textbf{Windows} and \textbf{Linux} operating systems, or you can get the source code and build the program yourself.
	\item \itemtitle{Easy to use}
		Intuitive tabbed interfaces of the program main window and sidebar help to speed up the treatment of the complete dataset or individual peaks.
	\item \itemtitle{Various supported instruments}
		\textbf{Davinci} accepts the data from the neutron instruments \textbf{POLI}, \textbf{HEiDi} and \textbf{MIRA} at \textbf{MLZ} as well as \textbf{6T2} at \textbf{LLB} and \textbf{TriCS} at \textbf{SINQ}.
	\item \itemtitle{Different peak integrations}
		Both the conventional and Lehmann-Larsen algorithms for the definition of the peak and background parameters are available.
	\item \itemtitle{Build-in text editor}
		To simplify the analysis of the experimental log and data files, \textbf{Davinci} has its build-in text editor with search functionality.
	\item \itemtitle{Multiple output formats}
		Davinci allows to save the extracted peak plots as graphics (.jpg, .pdf) as well as the output table as text (.csv, .hkl, .tb, .fli).
\end{itemize}
